%
% Modified by Megan Patnott
% Last Change: Jan 18, 2013
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Modified by Sameer Vijay
% Last Change: Wed Jul 27 2005 13:00 CEST
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Sample Notre Dame Thesis/Dissertation
% Using Donald Peterson's ndthesis classfile
%
% Written by Jeff Squyres and Don Peterson
%
% Provided by the Information Technology Committee of
%   the Graduate Student Union
%   http://www.gsu.nd.edu/
%
% Nothing in this document is serious except the format.  :-)
%
% If you have any suggestions, comments, questions, please send e-mail
% to: ndthesis@gsu.nd.edu
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
% Chapter 2
%

\chapter{Conclusion}

The operation of LHC opens a new era for experimental particle physics search with colliders. The great performance of general purpose detector CMS provides the possibilities to fully explore new physics. Through out this dissertation, the theory background for the search, an introduction of LHC and CMS, the detailed information about the data sets used, the reconstruction methods for the events in CMS and the search in two channels of LFV Higgs decays are presented. The focus is the physics search. 

  
The search for standard model Higgs lepton flavour violation decay on Large hadron collider with CMS detecter. One search on $\Hehad$ with $19.7~fb^{-1}$ 8 TeV data and a continue search on $\Hmuhad$ with $35.9~fb^{-1}$ 13 TeV. The results from both of the searches are presented, also the final results which combined with search in which the tau leptons decay electronically. The $H \to e \tau$ search gave the upper limit from the direct measurement for the first time. The combined limit on branching fraction in $\Hehad$ came as $B<0.69$ at 95\% CL and on Yukawa coupling as$Y_{e\tau}<2.4\times10^{-3}$. The continue search on $\Hmuhad$ with $35.9~fb^{-1}$ 13 TeV is also presented. Even though the excess observed in 8 TeV search in $H \to \mu \tau$ channel is gone, the combined result from 13 TeV search is the tightest limit so far. In $H \to \mu \tau$, a combined limit on  is $B<0.25\%$ and the upper limit on Yukawa coupling is $Y_{\mu\tau}<1.43\times10^{-3}$.   

The latest search for 125 GeV Higgs LFV decay $H \to \mu \tau$ is presented in the dissertation. While for the $H \to e \tau$ search, the 13 TeV results published together with $H \to \mu \tau$ search here~\cite{Sirunyan2018}. Though no significant excesses are observed in both $\mu\tau$ and $e\tau$ channel, compared to the $H \to e \mu$ channel, there is still huge room to explore in this topic. Whether or not LFV is observed, this is an important topic which has big influences on new physics searches.  









