%
% Modified by Megan Patnott
% Last Change: Jan 18, 2013
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Modified by Sameer Vijay
% Last Change: Wed Jul 27 2005 13:00 CEST
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Sample Notre Dame Thesis/Dissertation
% Using Donald Peterson's ndthesis classfile
%
% Written by Jeff Squyres and Don Peterson
%
% Provided by the Information Technology Committee of
%   the Graduate Student Union
%   http://www.gsu.nd.edu/
%
% Nothing in this document is serious except the format.  :-)
%
% If you have any suggestions, comments, questions, please send e-mail
% to: ndthesis@gsu.nd.edu
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
% Chapter 2
%

\chapter{Signal extraction and systematics}

\section{Boost decision trees method} \label{BDTchaper}

\section{statistical methods}

\section{Systematics}
Systematic uncertainties originated from different sources that experimentally or theoretically affects the physics results. These uncertainties are considered by the effects on the normalization and shape of the distribution of different processes. 

\subsection{Systematics used in $\Hmuhad$}
The systematic uncertainties considered in this analysis are summarized in Table.~\ref{tab:systematicsone} and Table.~\ref{tab:systematicstwo}. The uncertainty on muon trigger, identification and isolation together amounts  to 2\% and the hadronic tau lepton efficiency amounts to 5\%. The uncertainties on lepton selections that include trigger, ID, isolation efficiencies are estimated Tag and probe method with Z boson data sets~\cite{Khachatryan2011,Chatrchyan:2012xi,Khachatryan:2015hwa,Khachatryan:2015dfa,CMS:2016gvn}. The systematic uncertainty of b tagging veto is taken from the uncertainty of b tagging veto efficiency measurement, which adjusts b tagging veto performance in simulation to match data samples. The exact values used in each category of $t\bar{t}$ and single top samples are in Table.~\ref{tab:btaguncertainty}. The uncertainties on $Z\to\tau\tau$, WW, WZ, ZZ, $t\bar{t}$, single top backgrounds mainly come from the uncertainties on the cross section measurement of each process. The normalization uncertainty of $\mu$ fake $\tau$ scale factor measurement and the uncertainty on $Z\to \mu\mu$ process together amounts to 25\%. An additional shape uncertainty of muon misidentifying tau is extracted from the measurement of the scale factor and treats independently of hadronic tau decay modes. $Z\to \mu\mu$ is the main source that contributes to $\mu$ fake $\tau$.  The uncertainty of the misidentified lepton background is estimated from the matching of the same sign control region which is defined as region II in Table.~\ref{tab:fakeratediagram}. The 30\% on normalization uncorrelated between each category and additional 10\% partially correlated within each category is a conservative estimation. Only the tau shape uncertainties are considered, which are taken from the variations of the misidentified tau parameters in fitting.  Muon misidentified shape uncertainty is omitted as it would be negligible compared with the bin-by-bin uncertainty applied.  The shape uncertainties of jet energy scale is estimated by varying the fitting parameters of different sources that affect this scale by one $\sigma$. Tau energy scale is treated as shape uncertainties and each of the tau decay modes is considered as independently. Unclustered energy refers to the energy loses from the jets $\pt<10$ GeV and the PF candidates that are not included in the jets reconstruction. The unclustered energy uncertainty is considered independently for charged particles, photons, neutral hadrons and very forward particles.  The uncertainties on Higgs boson cross section is affected by the renormalization scales, factorization, parton distribution functions(PDF) and the strong coupling constant($\alpha_{s}$). These affections in normalization are taken from \cite{YR4}.The uncertainties on Higgs cross section also affect the acceptance and result in the migration of events between categories.  The bin-by-bin uncertainty is applied to account for the statistics uncertainties within each bin. These uncertainties are uncorrected between different bins and categories. The uncertainty of integrated luminosity~\cite{CMS-PAS-LUM-17-001}  amounts to 2.5\%.



\begin{table}[htpb]
\caption{Part one of the systematic uncertainties considered in $\Hmuhad$ analysis. All of the uncertainties listed in the systematic tables are correlated between categories besides the ones after the sign $\oplus$. These are the uncertainties correlated in within each category but independent between categories. The theoretical uncertainties related to the acceptance and migration of events are listed in a range. The negative or positive values indicate a anticorrelated or correlated between categories}

%\caption{Part one of the systematic uncertainties considered in $\Hmuhad$ analysis. Systematic uncertainties in the expected event yields. All uncertainties are treated as correlated between the categories, except those that have two values separated by the $\oplus$ sign. In this case, the first value is the correlated uncertainty and the second value is the  uncorrelated uncertainty for each individual category. Theoretical uncertainties on VBF Higgs boson production~\cite{YR4}  are also applied to VH production. Uncertainties on acceptance lead to migration of events between the categories, and can be correlated or anticorrelated between categories. Ranges of uncertainties for the Higgs boson production indicate the variation in size, from negative (anticorrelated) to positive (correlated)}
\label{tab:systematicsone}
\centering
\begin{tabular}{l*{4}{c}} \hline
Systematic  uncertainty            & $\PH\to\Pgm\tauh$  \\ \hline
Muon  trigger/identification/isolation         &       2\%             \\
Hadronic tau lepton efficiency                  &       5\%              \\
b tagging veto                                          &      2.0--4.5\%     \\
$\PZ\to\Pgt\Pgt$ + jets background         &    10\%$\oplus$5\%   \\
$\PW\PW, \PZ\PZ$ background              &     5\%$\oplus$5\%       \\
\ttbar\  background                                  &     10\%$\oplus$5\%             \\
Single top quark background                 &     5\%$\oplus$5\%  \\
$\Pgm\to\tauh$ background                                      &         25\%         \\
$\text{Jet}\to\tauh, \Pgm $ background             &  30\%$\oplus$10\%   \\
Jet energy scale                                                       &   3--20\% \\
\tauh energy scale                                                    &   1.2\%  \\\hline
\end{tabular}
\end{table}



\begin{table}[htpb]
\caption{Part two of the systematic uncertainties considered in $\Hmuhad$ analysis}
\label{tab:systematicstwo}
\centering
\begin{tabular}{l*{4}{c}} \hline
Systematic  uncertainty                                             & $\PH\to\Pgm\tauh$ \\ \hline

$\Pgm \to\tauh$ energy scale                                   &    1.5\%  \\
\Pgm\ energy scale                                                   &        0.2\%      \\
Unclustered energy scale                                         &        $\pm 1 \sigma$  \\
Renorm./fact. scales ({\Pg\Pg}H)   \cite{YR4}          &   \multicolumn{4}{c}{3.9\%}\\
Renorm./fact. scales (VBF and VH) \cite{YR4}         &   \multicolumn{4}{c}{0.4\%}\\
PDF + $\alpha_s$ ({\Pg\Pg}H)    \cite{YR4}             &   \multicolumn{4}{c}{ 3.2\%}\\
PDF + $\alpha_s$ (VBF and VH)   \cite{YR4}          &   \multicolumn{4}{c}{ 2.1\%}\\
Renorm./fact. acceptance ({\Pg\Pg}H)                     &   \multicolumn{4}{c}{$-3.0$\% -- $+2.0$\% } \\
Renorm./fact. acceptance (VBF and VH)                &   \multicolumn{4}{c}{$-0.3$\% -- $+1.0$\% } \\
PDF + $\alpha_s$ acceptance ({\Pg\Pg}H)              &   \multicolumn{4}{c}{ $-1.5$\% --  $+0.5$\%}\\
PDF + $\alpha_s$ acceptance (VBF and VH)          &   \multicolumn{4}{c}{ $-1.5$\% --  $+1.0$\%}\\
Integrated luminosity               &   \multicolumn{4}{c}{ 2.5\%  } \\ \hline
\end{tabular}
\end{table}

\begin{table}[htpb]
\caption{b tagging veto systematic uncertainty in each category}
\label{tab:btaguncertainty}
\centering
\begin{tabular}{lclclclcl}\hline
                       & 0 jet    &  1 jet       & 2 jets gg-enriched & 2 jets VBF-enriched \\\hline
$t\bar{t}$        &  \NA    &  2.45\%    &4.37\%                   & 2.59\%     \\   
$t$   & \NA     &  2.11\%    & 3.07\%                   & 1.98\%   \\\hline
\end{tabular}
\end{table}







\subsection{Systematic uncertainties in $\Hehad$}

The systematic uncertainties affect the $\Hehad$ analysis are summarized in Table.~\ref{tab:systematics_had}, \ref{tab:theory_systematics} and \ref{tab:shape_systematics}, which includes the ones affect the normalization and the ones affects the shape of $\mcol$ distribution. The uncertainty of the electron measurements, which include the trigger, ID and isolation come from the Tag and Probe measurement with Z boson datasets \cite{CMS:2011aa,Khachatryan:2015dfa}. The uncertainties from the $\PZ \to \tau \tau$ is from the uncertainty of the cross section measurement~\cite{Chatrchyan:2014mua} and the $\tau$ identification in the embedded technique. The normalization uncertainty on $\PZ \to \Pgm \Pgm$ amounts to 30\% which is the from the measurement of cross section and statistics uncertainty in the yields. An extra 5\% shape uncertainty due to the mismeasured energy of the electron reconstructed as $\Pgt$ in $\PZ \to \Pe\Pe$ background.  The shift in $\mcol$ distribution is measured by comparison between data and MC simulation. The uncertainty in misidentified tau lepton background is 30\% normalization uncertainty correlated between categories and shape uncertainties. The shape uncertainties is obtained by varying the parameters from fitting the fake ratio one standard deviation.   The uncertainty from the pileup process are estimated by varying the total inelastic cross section by $\pm5$ percentage~\cite{Chatrchyan:2012nj}. The uncertainty from Diboson, single top quark background is taken from the measurement of the cross section. In $t\bar{t}$ background, the uncertainty in 0 jet, 1 jet category are taken from the cross section measurement, in 2  jets category, an extra 33\% uncertainty uncorrelated between categories is added due to the statistical uncertainty. The luminosity uncertainty amounts to 2.6\%.  Jet energy scale(JES) and resolution is measured with $\gamma/\PZ+jets$ and dijet data~\cite{CMS-JME-10-011}. The uncertainty from JES is applied as a function of $\pt$ and $\eta$. Jet energy resolution(JER) uncertainty is obtained by smearing jets energy as a function of $\pt$ and $\eta$. Both JES and JER affect the shape of $\mcol$ distribution and are taken as shape uncertainties. The energy of the jets below 10 GeV and PF objets that are not clustered are accounted as the unclustered energy scale, which is also taken as shape uncertainties. The uncertainty of $\tau_{h}$ energy scale is from the comparing $\PZ \to \tau\tau$ distruction between data and MC sample and applied as a shape uncertainty. The theoretical uncertainties considered in the $\Hehad$ analysis are listed in Table.~\ref{tab:theory_systematics}. There are several sources that contribute to the theoretical uncertainties and considered fully correlated between LFV Higgs and SM Higgs production. The uncertainty in Parton distribution function is obtained by counting the yields with different PDFs,  CT10~\cite{Nadolsky:2008zw}, MSTW~\cite{Martin:2009iq}, NNPDF~\cite{Ball:2010de}  from the recommendation in PDF4LHC~\cite{Botje:2011sn}. The uncertainty in renormalization and factorization scales are from scaling up and down by a factor of two to their normal values($\mu_{R}=\mu_{F}=M_{H}/2$). The uncertainty in underlying events and parton shower is estimated by checking with different PYTHIA tunes. The theoretical uncertainties are all correlated or anticorrelated which have a minus superscript and are the results of the events migration.   




\begin{table*}[hbt]
 \centering
 \caption{The normalization systematic uncertainties considered in $\Hehad$ analysis. The uncertainties are correlated between categories besides the ones after $\oplus$. These uncertainies are uncorrelated between categories. }
  \label{tab:systematics_had}
\begin{tabular}{l|c|c|c} \hline
Systematic uncertainty                  & \multicolumn{3}{c}{\PH$\to \Pe\tauh$}      \\ 
                                                      & 0-jet       & 1-jet        & 2-jet                 \\ \hline
Electron trigger/ID/isolation           &  1\%           &   1\%         &  2\%                       \\
Efficiency of $\tauh$                      &  6.7\%         &  6.7\%        & 6.7\%                      \\
$\PZ\to \Pgt \Pgt$ background    & 3\%$\oplus$5\% & 3\%$\oplus$5\%& 3\%$\oplus$10\%            \\
$\PZ\to \Pe\Pe$ background                      & 30\%           &  30\%         & 30\%                       \\

Misidentified leptons background                   & 30\%           &  30\%         & 30\%                       \\
Pileup                                           & 4\%           & 4\%          & 2\%                       \\
$\PW\PW,\PW\PZ,\PZ\PZ\mathrm{+jets}$ background                 & 15\%           &  15\%         & 15\%                       \\
$\ttbar$ background                     & 10\%           &  10\%         & 10\%$\oplus$33\%           \\
Single top quark background       & 25\%           &  25\%         & 25\%                      \\
Luminosity                                    & 2.6\%          &  2.6\%        & 2.6\%                      \\ \hline
\end{tabular}
\end{table*}


\begin{table}[hbtp]
 \centering
 \caption{The systematic uncertainties that affect the shape of $\mcol$ distribution. }
  %\caption{Systematic uncertainties in the shape of the signal and background distributions, expressed in percentage. The systematic uncertainty and its implementation are described in the text.}
  \label{tab:shape_systematics}
  \begin{tabular}{lclc} \hline
Systematic Uncertainty                                 &   $\PH \to \Pe \tauh$                   \\ \hline
$Z \to \Pe\Pe$ bias                                       &   5\%                                         \\
Jet energy scale                                           &    3\%--7\%                                       \\
Jet energy resolution                                    &    1\%--10\%                                       \\
Unclustered energy scale                             &    10\%                                       \\
$\tauh$ energy scale                                    &    3\%                                         \\    \hline
  \end{tabular}
\end{table}



\begin{table*}[hbtp]
 \centering
 \caption{Theoretical uncertainties that affects the Higgs boson production cross section. These uncertainties are correlated or anticorrelated(with minus sign superscript) between all of the categories.}
 % \caption{Theoretical uncertainties in percentage for the Higgs boson production cross section for each production process and category. All uncertainties are treated as fully correlated between categories except those denoted by a negative superscript which are fully anticorrelated due to the migration of events.}
  \label{tab:theory_systematics}
  \begin{tabular}{l|l|l|l|l|l|l} \hline
Systematic uncertainty                  &  \multicolumn{3}{c|}{Gluon fusion} &  \multicolumn{3}{c}{Vector boson fusion}  \\ \cline{2-7}
                                &    0-jet  & 1-jet  & 2-jet   & 0-jet & 1-jet  & 2-jet  \\ \hline
Parton distribution function         &    $9.7$\%  &  $9.7$\% &   $9.7$\% & $3.6$\%  &   $3.6$\%  &  $3.6$\%  \\
Renormalization/factorization scale           &    $8$\%    &  $10$\%   &  $30^{-}$\%   & $4$\%     &   $1.5$\%  & $2$\%   \\
Underlying event/parton shower  &   $4$\%     & $5^{-}$\%   &  $10^{-}$\%   & $10$\%    &   $<$1\%    & $1^{-}$\%   \\ \hline
  \end{tabular}
\end{table*}


       




